The Impact of Interview Disruptions on Data Quality in Social Surveys

### 2024-12-02 paper/paper.qmd
update paper

---
title: "The Impact of Interview Disruptions on Data Quality in Social Surveys"
subtitle: "Family Interference and Interview Methods Found to Significantly Affect Respondent Comprehension and Survey Data Quality"
author: 
  - Dezhen Chen
thanks: "Code and data are available at: https://github.com/1Dezhenchen/The-Influence-of-Interview-Disruptions-on-Respondent-Data-Quality-in-Social-Surveys."
date: today
date-format: long
abstract: "In social surveys, disruptions during interviews can profoundly impact the quality of respondent data, thereby affecting the overall reliability of survey results. This study employs Bayesian hierarchical logistic regression to analyze the influence of a diverse range of factors—including the type of disruption, presence of family members, interview methodology, interviewer characteristics, and respondent attitudes—on response quality and accuracy. Our findings indicate that various forms of disruptions uniquely impact data quality, with some conditions proving more detrimental than others. These insights are pivotal for refining survey methodologies and optimizing interview conditions, ultimately improving the reliability and validity of collected data."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "The Impact of Interview Disruptions on Data Quality in Social Surveys"
subtitle: "Family Interference and Interview Methods Found to Significantly Affect Respondent Comprehension and Survey Data Quality"
author: 
  - Dezhen Chen
thanks: "Code and data are available at: https://github.com/1Dezhenchen/The-Influence-of-Interview-Disruptions-on-Respondent-Data-Quality-in-Social-Surveys."
date: today
date-format: long
abstract: "In social surveys, disruptions during interviews can profoundly impact the quality of respondent data, thereby affecting the overall reliability of survey results. This study employs Bayesian hierarchical logistic regression to analyze the influence of a diverse range of factors—including the type of disruption, presence of family members, interview methodology, interviewer characteristics, and respondent attitudes—on response quality and accuracy. Our findings indicate that various forms of disruptions uniquely impact data quality, with some conditions proving more detrimental than others. These insights are pivotal for refining survey methodologies and optimizing interview conditions, ultimately improving the reliability and validity of collected data."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---
